An Abstraction-based Approach to Network Synthesis

### 2016-11-02 paper/abstraction/paper.tex
update section 4

%=====================================================
%
%
%  **Propane Language**
%
%
%=====================================================

\section{Methane overview}
\label{sec:propane}

@@

Suppose now that we want to disallow paths with valleys (\IE, paths that go down and then up at some point). Such a constraint can be added to the routing policy simply:
\begin{code}
\Define ValleyFree =
    \True \Path \Novalley(\{TL,TG\},\{AL,AG\},\{S\})
\end{code}
\noindent%

@@

\subsection{Language}

@@

\section{Compilation}
\label{sec:compilation}

We borrow the intermediate graph-based representation from Propane:

\begin{easylist}[itemize]
& Show compilation from language to RIR

& Show compilation from RIR to Product Graph
&& Note that preferences are general, and it could potentially
   use any implementation (including SDN). But for the sake of
   simplicity, we will assume a BGP backend like Propane.
\end{easylist}

@@

  \begin{minipage}[t]{.6\linewidth}
  \hdr{Concrete Product Graph}{}
  %\includegraphics[width=.65\columnwidth]{figures/example3}
  \end{minipage}%
  \begin{minipage}[t]{.4\linewidth}
  \hdr{Abstract Product Graph}{}

    \begin{tikzpicture}
      \draw [] (0, 0) circle [radius=0.45] node {start};
      \draw [] (-1, -1) circle [radius=0.45] node {$(S,0,0)$};
      %\draw [] (0, .45) -- (0, 2.05);
    \end{tikzpicture}

@@

\section{Abstraction}
\label{sec:abstraction}

\begin{easylist}[itemize]
& Define abstractions more formally,
&& e.g., homomorphism between graphs + node/edge constraints
&& Use the datacenter example from before
&& First define the concretization function for translating the abstract policy
   into the concrete policy
&& Next, show the Product Graph for both the concrete and abstract policies.

& Show/Define safety analysis simulation relation for both concrete and abstract product graphs
  and how it holds for both.
&& Theorem: if safety analysis holdls in the abstract graph, it holds for the concrete one,
   and the preferences are consistent.

& Show/Define compilation to abstract BGP policies. Give concretization function,
  and compilation definition.

@@

\begin{figure*}[t!]
  \begin{minipage}[t]{.5\linewidth}%
  \begin{tikzpicture}
    \inference{0}{L$(j,k)$}{$\vDash e_1 > 0$}{S$(min(j*k,e_1),1)$}
    \inference{10}{A$(j,k)$}{$e_2 > 0$}{A$(1,min(j,e2))$}
  \end{tikzpicture}
  \end{minipage}

  %
  \vspace*{3em}
  %
  \begin{minipage}[t]{.5\linewidth}%
  \begin{tikzpicture}
    \inference{0}{L$(j,k)$}{$e_1=n$}{A$(min(j*k,n),1)$}
    \inference{10}{L$(j,k)$}{$e_1=n$}{A$(1,j)$}
  \end{tikzpicture}
  \end{minipage}

  %
  \vspace*{3em}
  %
  \begin{minipage}[t]{.5\linewidth}%
  \begin{tikzpicture}
    \inference{0}{L$(j,k)$}{$e_1 > 0$, $e_2 > 0$}{S$(min(j*k,n-\dfrac{(m-j)*e_1}{e_2}),1)$}
  \end{tikzpicture}
  \end{minipage}

  %
  \vspace*{3em}
  %
  \begin{minipage}[t]{.5\linewidth}%
  \begin{tikzpicture}
    \inference{10}{L$(j,k)$ ~~~ L$(j- m ~\text{mod}~ \big(\dfrac{n}{e_1}\big),1)$}{$e_1 > 0$, $e_2 > 0$}{}
  \end{tikzpicture}
  \end{minipage}
  %
  \vspace*{1em}
  \hrule
  \vspace*{1em}
  \caption{Abstract k-disjoint path analysis inference rules.}
  \label{fig:abstract-analysis}
  %\vspace{-1em}
\end{figure*}

@@

\begin{figure}[t!]
  \begin{center}
      \begin{tabular}{| l l | c | c | c |}
      \hline
      \textbf{Topology} & \textbf{Variant} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
      Fattree
         & Google &  & \cmark & \cmark  \\
         & Facebook &  & \cmark & \cmark \\
         & F10 &  & \cmark & \cmark \\ \hline
      Recursive
         & BCube & $k$ & \cmark & \xmark \\
         & DCell & $k$ & \cmark & \xmark \\ \hline
         %& HCN & $h$ & \cmark & \xmark \\
      Hypercube
         & Standard & $N$ & \cmark & \cmark \\
         & HyperX & $L$ & \cmark & \cmark \\ \hline
      Random \footnote{foo}
         & Scafida &  & ??? & ??? \\
         & JellyFish &  & ??? & ??? \\

      \hline
      \end{tabular}
  \end{center}
  \caption{Abstract Analysis Precision.}
  \label{fig:analysis-precision}
\end{figure}

@@

\para{Random Network Topologies}

Random networks such as Scafida and Jellyfish have seen a great deal of interest in academia. These topologies were designed with an eye towards incremental expansion and are based on probabilistic arguments of bisection bandwidth in random regular graphs. However, because the topologies are created randomly, there are no hard guarantees on the connectivity between different routers. We can trivially represent these networks using a \emph{one big switch} abstraction for the entire network.

>>>>

%=====================================================
%
%
%  **Methane Overview**
%
%
%=====================================================

\section{Methane overview}
\label{sec:overview}

@@

Suppose now that we want to disallow paths with valleys (\IE, paths that go down and then up at some point). Such a constraint can be added to the routing policy in \sysname:
\begin{code}
\Define ValleyFree =
    \True \Path \Novalley(\{TL,TG\},\{AL,AG\},\{S\})
\end{code}
\noindent%

@@

@@

\section{Configuration Synthesis}
\label{sec:compilation}

Configuration synthesis for network configurations is challenging for a number of reasons. First, although \sysname polices specify stable network-wide routing behavior, actual configurations are per-device and run distributed algorithms to compute routes. Thus the compiler must ensure that the result of the distributed computation matches the policy. Furthermore the distributed computation must compute the correct paths under all possible combinations of failures. Second, \sysname must find configurations that work across any valid concrete network topology matching the abstraction provided as input. Finally, \sysname must ensure that the resulting configurations can be evolved incrementally so that local changes to the topology ensure that only local changes to configurations are required to ensure global routing correctness.

In this section, we introduce the idea of topology abstraction, describe how \sysname synthesizes network configurations over these abstractions, and formalize the guarantees provided by \sysname.

\subsection{Methane Language}

The syntax introduced in \S\ref{sec:overview} is just syntactic sugar for a core language based on regular expressions. Figure~\ref{fig:syntax} shows a simplified version of the core \sysname syntax that omits some details such as aggregation. The full langauge definition can be found in the appendix. A policy has one or more constraints, each of which consists of a test on the type of traffic being matched and a corresponding set of preferred regular expressions describing network paths. Regular expressions are defined over network locations, where each location is either a router inside the operators network, or an external neighbor. There are two special characters \In~ and \Out, which match any internal and external location respectively. There are two types of predicates: a test for a concrete prefix $d.d.d.d/[d..d]$ matches an IP prefix with value $d.d.d.d$ and length in the range $[d..d]$ where metavariable $d$ represents an integer. For example, the IP prefix 148.0.1.0/[24..32] would match traffic destined for IP address 148.0.1.* with a subnet length between 24 and 32 bits. \ryan{this needs to be explained clearer}.

Converting from the high-level syntax from \S\ref{sec:overview} to the core syntax is straightforward. For example, the predicate $\True$ becomes $0.0.0.0/[0..32]$. Preferences are lifted to the top level of the regular expression when unambiguous. For example, the constraint $\Exit(\sf{Peer1} \Prefer \sf{Peer2})$ becomes $\Exit(\sf{Peer1}) \Prefer \Exit(\sf{Peer2})$ before being rewritten into regular expressions. Each modular set of constraints are joined prefix-by-prefix by taking the intersection of their constraints. For example, the data center policy from \S\ref{sec:overview} would result in the following \sysname policy:
%
\begin{code}
\$PG  \Path \End(TG) & !transit(\Out,\Out),
\$PL  \Path \End(TL) & \Always(\In) & !transit(\Out,\Out),
\True \Path 
    \Exit(Peer1) & !transit(\Out,\Out) \Prefer 
    \Exit(Peer2) & !transit(\Out,\Out)
\end{code}
\noindent%
%
Finally, each constraint desugars to a regular expression. For example, the constraint $\Always(\In)$ becomes $\In^*$ and the constraint $\End({\small \mathsf{T0}})$ becomes $\Sigma^* \cdot \sf{T0}$.

\subsection{Topology Abstraction}

\subsection{Configuration Synthesis}

\subsection{Substitution Theorem}

\begin{easylist}[itemize]
& Define abstractions more formally,
&& e.g., homomorphism between graphs + node/edge constraints

&& First show how to compile to the Product Graph, and from there to the ABGP
&& Show/Define safety analysis simulation relation for both concrete and abstract product graphs
  and how it holds for both.
&& Next define the concretization & subst. functions for translating the abstract policy
   into the concrete policy, using the ABGP example for reference

&& Theorem: if safety analysis holdls in the abstract graph, it holds for the concrete one,
   and the preferences are consistent.

\begin{figure}[t]\small
  \begin{minipage}[t]{\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{constraints} \\
     t       &::=& \$x & \textit{template variable} \\
         &\BNFALT& d.d.d.d/[d..d] & \textit{prefix test} \\
     r       &::=& l & \textit{location} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT r & \textit{path negation} \\
         &\BNFALT& r^* & \textit{iteration} \\
  \end{array} \]%

  \end{minipage}
  \vspace{1em}
  \caption{Simplified \sysname syntax.}
  \label{fig:syntax}
  %\vspace{-1em}
\end{figure}%

@@

  \vspace{2em}
  \begin{minipage}[t]{.6\linewidth}
    \hdr{Concrete Product Graph}{}
    \includegraphics[width=.9\columnwidth]{figures/pg-con}
  \end{minipage}%
  \begin{minipage}[t]{.4\linewidth}
  \hdr{Abstract Product Graph}{}
    \includegraphics[width=.9\columnwidth]{figures/pg-abs}

@@

\section{Analysis}
\label{sec:analysis}

@@

\begin{figure*}[t!]
  \begin{minipage}[t]{.5\linewidth}%
  \begin{tikzpicture}
    \inference{0}{L$(j,k)$}{$\vDash e_1 > 0$}{S$(min(j*k,e_1),1)$}
    \inference{5}{A$(j,k)$}{$e_2 > 0$}{A$(1,min(j,e2))$}
    \inference{10}{L$(j,k)$}{$e_1=n$}{A$(min(j*k,n),1)$}
    \inference{15}{L$(j,k)$}{$e_1=n$}{A$(1,j)$}
  \end{tikzpicture}
  \end{minipage}

  %
  \vspace*{3em}
  %
  \begin{minipage}[t]{.5\linewidth}%
  \begin{tikzpicture}
    \inference{0}{L$(j,k)$}{$e_1 > 0$, $e_2 > 0$}{S$(min(j*k,n-\dfrac{(m-j)*e_1}{e_2}),1)$}
    \inference{10}{L$(j,k)$ ~~~ L$(j- m ~\text{mod}~ \big(\dfrac{n}{e_1}\big),1)$}{$e_1 > 0$, $e_2 > 0$}{}
  \end{tikzpicture}
  \end{minipage}

  \vspace*{1em}
  \hrule
  \vspace*{1em}
  \caption{Abstract k-disjoint path analysis inference rules.}
  \label{fig:abstract-analysis}
  %\vspace{-1em}
\end{figure*}

@@

\begin{figure}[t!]
  \begin{center}
      \begin{tabular}{| l | c | c | c |}
      \hline
      \textbf{Topology} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
      Google Fattree & & \cmark & \cmark  \\ \hline
      Facebook Fattree & & \cmark & \cmark \\ \hline
      Microsoft Fattree & & & \\ \hline
      F10 Fattree & & \cmark & \cmark \\ \hline
      BCube & $k$ & \cmark & \xmark \\ \hline
      DCell & $k$ & \cmark & \xmark \\ \hline
         %& HCN & $h$ & \cmark & \xmark \\
      Butterfly & $n$ & \cmark & \cmark \\ \hline
      Hypercube & $N$ & \cmark & \cmark \\ \hline
      HyperX & $L$ & \cmark & \cmark \\ \hline
      \end{tabular}
  \end{center}
  \caption{Abstract Analysis Precision.}
  \label{fig:analysis-precision}
\end{figure}

%\begin{figure}[t!]
%  \begin{center}
%      \begin{tabular}{| l l | c | c | c |}
%      \hline
%      \textbf{Topology} & \textbf{Variant} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
%      Fattree
%         & Google &  & \cmark & \cmark  \\
%         & Facebook &  & \cmark & \cmark \\
%         & F10 &  & \cmark & \cmark \\ \hline
%      Recursive
%         & BCube & $k$ & \cmark & \xmark \\
%         & DCell & $k$ & \cmark & \xmark \\ \hline
%         %& HCN & $h$ & \cmark & \xmark \\
%      Hypercube
%         & Standard & $N$ & \cmark & \cmark \\
%         & HyperX & $L$ & \cmark & \cmark \\ \hline
%      Random \footnote{foo}
%         & Scafida &  & ??? & ??? \\
%         & JellyFish &  & ??? & ??? \\
%      \hline
%      \end{tabular}
%  \end{center}
%  \caption{Abstract Analysis Precision.}
%  \label{fig:analysis-precision}
%\end{figure}

@@

%\para{Random Network Topologies}
%
%Random networks such as Scafida and Jellyfish have seen a great deal of interest in academia. These topologies were designed with an eye towards incremental expansion and are based on probabilistic arguments of bisection bandwidth in random regular graphs. However, because the topologies are created randomly, there are no hard guarantees on the connectivity between different routers. We can trivially represent these networks using a \emph{one big switch} abstraction for the entire network.
